\pkg{partykit}: A Toolbox for Recursive Partytioning

### 2009-02-25 pkg/inst/slides/useR-2009_abstract.tex
renamed and added slightly modified abstract for DSC 2009
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@127 255f4249-2263-4417-b1ea-8498779e27a7

Recursive partitioning methods, or simply ``trees'', are simple yet powerful
methods for capturing regression relationships. Since the publication of the
automated interaction detection (AID) algorithm in 1964, many extentions,
modifications, and new approaches have been suggested in both the statistics
and machine learning communities. Most of the standard algorithms are
available to the \proglang{R} user, e.g., through packages
\pkg{rpart} \citep{PKG:rpart},
\pkg{RWeka} \citep{PKG:RWeka},
\pkg{party} \citep{PKG:party}, or
\pkg{mvpart} \citep{PKG:mvpart}.

@@

To overcome these difficulties, the \pkg{partykit} package \citep{PKG:partykit} offers a 
unified representation of tree objects along with \code{predict()}, 
\code{print()}, and \code{plot()} methods. Trees are represented through 
a new flexible class \class{party} which can, in principle, capture
all trees mentioned above but can also accomodate multi-way or functional
splits, as well as complex models in (leaf) nodes. The package is currently
under development at R-Forge but already provides conversion methods for
trees of classes \class{rpart}, \class{J48}, and \class{pmmlTreeModel}
as well as a re-implementation of conditional inference trees \citep{Hothorn:2006:JCGS}.

>>>>

Recursive partitioning methods, or simply ``trees'', are simple yet powerful
methods for capturing regression relationships. Since the publication of the
automated interaction detection (AID) algorithm in 1964, many extentions,
modifications, and new approaches have been suggested in both the statistics
and machine learning communities. Most of the standard algorithms are
available to the \proglang{R} user, e.g., through packages
\pkg{rpart} \citep{partykit:rpart},
\pkg{RWeka} \citep{partykit:RWeka},
\pkg{party} \citep{partykit:party}, or
\pkg{mvpart} \citep{partykit:mvpart}.

@@

To overcome these difficulties, the \pkg{partykit} package \citep{partykit:partykit} offers a 
unified representation of tree objects along with \code{predict()}, 
\code{print()}, and \code{plot()} methods. Trees are represented through 
a new flexible class \class{party} which can, in principle, capture
all trees mentioned above but can also accomodate multi-way or functional
splits, as well as complex models in (leaf) nodes. The package is currently
under development at R-Forge but already provides conversion methods for
trees of classes \class{rpart}, \class{J48}, and \class{pmmlTreeModel}
as well as a re-implementation of conditional inference trees \citep{partykit:Hothorn+Hornik+Zeileis:2006}.
